Exponential Integrals\\ [1ex]

### 2022-01-19 draft2.tex
add general equation for cubic polynomial

>>>>

\section{Resurgence for degree $3$ polynomials}

Let $f$ be a degree $3$ polynomial, and $x_{\alpha_1},x_{\alpha_2}$ its critical points (not necessarily distinguished). Then \[I(z)=\int_{\mathcal{C}_{\alpha}}e^{-zf}dt\] is a solution of a second order ODE with regular/irregular singularity at zero/infinity. In particular, only two cases can occur: let $f(t)=a_1t^3+a_2t^2+a_3t+a_4$
\begin{enumerate}
\item if $a_2=0$, \begin{equation} I''+2a_4 I'+\left(a_4^2+\frac{4}{27}\frac{a_3^3}{a_1}\right)I+\frac{I'}{z}+\frac{a_4}{z}I-\frac{1}{9z^2}=0
\end{equation}
\item if $a_2=a_3=0$, $I$ solves
\begin{equation}
I''+aI'+(aa_4-a_4^2)I+\frac{4+9e}{3}\frac{I'}{z}+\frac{a+2a_4+9a_4e}{3}\frac{I}{z}+\frac{e}{z^2}I=0
\end{equation}
for every $a,e\in\C$, which is equivalent to say $I$ is a solution of
\begin{equation}
I'+\left(a_4+\frac{3}{z}\right)I=0
\end{equation} 
\end{enumerate}
